Strings functions analysis

### 2022-08-28 article.tex
all js functions added
all go functions added

>>>>

    \textbf{Go}: Clone, Compare, Contains, ContainsAny, ContainsRune, Count, Cut, EqualFold, Fields, FieldsFunc, func, HasPrefix, HasSuffix, Index, IndexAny, IndexByte, IndexFunc, func, IndexRune, Join, LastIndex, LastIndexAny, LastIndexByte, LastIndexFunc, func, Map, func, Repeat, Replace, ReplaceAll, Split, SplitAfter, SplitAfterN, SplitN, Title, ToLower, ToLowerSpecial, ToTitle, ToTitleSpecial, ToUpper, ToUpperSpecial, ToValidUTF8, Trim, TrimFunc, func, TrimLeft, TrimLeftFunc, func, TrimPrefix, TrimRight, TrimRightFunc, func, TrimSpace, TrimSuffix.

    \textbf{C#}:

    \textbf{Swift}:

    \textbf{PHP}:

    \textbf{Rust}:
